---
title: "Tovar-Ruben-ADA-Homework-2"
author: "Ruben Tovar"
date: "3/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```{r}


```

####HOMEWORK 2###

###CHALLENGE_1####
```
f<-(IMDB_movies)

f

g <- as_tibble(f)
```
###Challenge 1.1###
```
g2<- filter(g, startYear>=1920,startYear<=1979,runtimeMinutes<240) %>% mutate(decade=case_when(
startYear>=1920 & startYear<1930 ~ "20",
startYear>=1930 & startYear<1940 ~ "30",
startYear>=1940 & startYear<1950 ~ "40",
startYear>=1950 & startYear<1960 ~ "50",
startYear>=1960 & startYear<1970 ~ "60",
startYear>=1970 & startYear<1980 ~ "70"))

g2
```
###Challenge 1.2###
```
p <- ggplot(data = g2, aes(x = runtimeMinutes)) + 
geom_histogram() + facet_wrap(~decade, nrow=2)

p
```
###Challenge 1.3###
```
results<-g2 %>%
  group_by(decade) %>%
mutate(mean=mean(runtimeMinutes), sd=sd(runtimeMinutes))
```
###Challenge 1.4###
```
newg<-g2 %>%
  group_by(decade) %>%
  sample_n(size=100) %>%
mutate(mean=mean(runtimeMinutes), sd=sd(runtimeMinutes), SE=sd/sqrt(100))
```

###Challenge 1.5###
```
m<-g2 %>%
  sample_n(size=100) %>%
mutate(mean=mean(runtimeMinutes), sd=sd(runtimeMinutes), SE=sd/sqrt(100))
```

###Challenge 1.6###
```
m <-mean(g2$runtimeMinutes)
k <- 10000 # number of samples
n <- 100 # size of each sample
s <- list(length = k) # create a dummy variable to hold each sample
for (i in 1:k) {
  s[[i]] <- sample(m, size = n, replace = FALSE)
} 
head(s)


sd<-sd(g2$runtimeMinutes)
k <- 10000 # number of samples
n <- 100 # size of each sample
s <- list(length = k) # create a dummy variable to hold each sample
for (i in 1:k) {
  s[[i]] <- sample(sd, size = n, replace = FALSE)
} 

head(s)
```

###CHALLENGE 2###
```
l = 18
probset <- dpois(x = x, lambda = l)
barplot(probset, names.arg = x, 
        space = 0, xlab = "x", ylab = "Pr(X = x)", 
        main = paste0("Probability Mass Function\nlambda = ", l))
```

###What is the probability that she will hear 13 or fewer calls during any given session?###
```
ppois(13,lambda=18)
```
###What is the probability that she will hear no calls in a session?
```
ppois(0,lambda=18)
```
###What is the probability that she will hear exactly 7 calls in a session?
```
dpois(7,18)
```
###What is the probability that she will hear more than 20 calls in a session?
```
1-ppois(20, lambda=18)
```
###Plot the relevant Poisson mass function over the values in range 0 ≤  x ≤ 40. ≤ 
```
y <- 0:40
l = 18
poisdist <- dpois(x = y, lambda = l)
barplot(poisdist, names.arg = y, 
        space = 0, xlab = "x", ylab = "Pr(X = x)", 
        main = paste0("Probability Mass Function\nlambda = ", l))
```
###Using the rpois() function, simulate 520 results from this distribution (i.e., 10 full years of Saturday monitoring sessions).
```
sim<-rpois(520, l)
```
###Plot the simulated results using the histogram() function from the {mosaic} package and use xlim() to set the horizontal limits to be from 0 to 40. How do your simulated results compare to the shape of the probability mass function you plotted above?
```
hist(sim, xlim = c(0,40))

y <- 0:40
l = 18
poisdist <- dpois(x = y, lambda = l)
barplot(poisdist, names.arg = y, 
        space = 0, xlab = "x", ylab = "Pr(X = x)", 
        main = paste0("Probability Mass Function\nlambda = ", l))
```

###CHALLENGE 3###
```
library(curl)

f <- curl("https://raw.githubusercontent.com/difiore/ADA-datasets/master/zombies.csv")
d <- read_csv(f, col_names = TRUE) # creates a "tibble"
```
###Calculate the population mean and standard deviation for each quantitative random variable (height, weight, age, number of zombies killed, and years of education).

###Mean
```
(pop_mean_height <- mean(d$height)) 
(pop_mean_weight <- mean(d$weight)) 
(pop_mean_age <- mean(d$age)) 
(pop_mean_zombies_killed <- mean(d$zombies_killed))
(pop_mean_years_of_education <- mean(d$years_of_education)) 
```
###Standard Deviations
```
(pop_var_height <- var(d$height)) 
(pop_var_weight <- var(d$weight)) 
(pop_var_age <- var(d$age)) 
(pop_var_zombies_killed <- var(d$zombies_killed))
(pop_var_years_of_education <- var(d$years_of_education)) 
```
###Use {ggplot2} and make scatterplots of height and weight in relation to age. Do these variables seem to be related? (YES) In what way? (LINEAR RELATIONSHIP)
```
library(ggplot2)
```
# Basic scatter plot height
```
(h <- ggplot(d, aes(x=height, y=age)) + geom_point())
```
# Basic scatter plot weight
```
(w <- ggplot(d, aes(x=weight, y=age)) + geom_point())
```
###Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not?

###Histogram###
```
histogram(d$height)
histogram(d$weight)
histogram(d$age)
histogram(d$zombies_killed)
histogram(d$years_of_education)
```
###QQ Plot###
```
qqnorm(d$years_of_education, main = "QQ Plot - Random Normal Variable")
qqline(d$years_of_education, col = "gray")


qqnorm(d$age, main = "QQ Plot - Random Normal Variable")
qqline(d$age, col = "gray")

 p<- ppoints(length(h)) # the `ppoints()` function generates evenly distributed points between 0 and 1

head(p)
```
###Now use the sample_n() function from {dplyr} to sample ONE subset of 30 zombie apocalypse survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable and construct the 95% confidence interval for each mean. You can use either the standard normal or a Student’s t distribution to derive the critical values needed to calculate the lower and upper limits of the CI.####

```
new_sample <- sample_n(d, size = n)

sset.seed(30)
s <- sample_n(d$height, size = 30, replace = FALSE)
(m <- mean(s))
(sd <- sd(d$height))
(se <- sd/sqrt(30))
percent_ci <- 95
alpha <- 1 - percent_ci / 100 # alpha = 0.05
lower <- m + qnorm(alpha / 2) * se
```

###where qnorm(alpha /2) is the 2.5% quantile of the standard normal distribution
```
upper <- m + qnorm(1 - alpha / 2) * se
```
###where qnorm(1 - alpha / 2) is the 97.5% quantile of the standard normal distribution
```
ci <- c(lower, upper)
ci
s2 <- sample_n(d$weight, size = 30, replace = FALSE)
(m <- mean(s))
(sd <- sd(d$weight))
(se <- sd/sqrt(100))
percent_ci <- 95
alpha <- 1 - percent_ci / 100 # alpha = 0.05
lower <- m + qnorm(alpha / 2) * se
```
###where qnorm(alpha /2) is the 2.5% quantile of the standard normal distribution
```
upper <- m + qnorm(1 - alpha / 2) * se
```
###where qnorm(1 - alpha / 2) is the 97.5% quantile of the standard normal distribution
```
ci2 <- c(lower, upper)
ci2

s3 <- sample_n(d$age, size = 30, replace = FALSE)
(m <- mean(s))
(sd <- sd(d$age))
(se <- sd/sqrt(30))
percent_ci <- 95
alpha <- 1 - percent_ci / 100 # alpha = 0.05
lower <- m + qnorm(alpha / 2) * se
```
###where qnorm(alpha /2) is the 2.5% quantile of the standard normal distribution
```
upper <- m + qnorm(1 - alpha / 2) * se
```
###where qnorm(1 - alpha / 2) is the 97.5% quantile of the standard normal distribution
```
ci3 <- c(lower, upper)
ci3

s4 <- sample_n(d$zombies_killed, size = 30, replace = FALSE)
(m <- mean(s))
(sd <- sd(d$zombies_killed))
(se <- sd/sqrt(30))
percent_ci <- 95
alpha <- 1 - percent_ci / 100 # alpha = 0.05
lower <- m + qnorm(alpha / 2) * se
```
###where qnorm(alpha /2) is the 2.5% quantile of the standard normal distribution
```
upper <- m + qnorm(1 - alpha / 2) * se
```
###where qnorm(1 - alpha / 2) is the 97.5% quantile of the standard normal distribution
```
ci4 <- c(lower, upper)
ci4

s5 <- sample_n(d$years_of_education, size = 30, replace = FALSE)
(m <- mean(s))
(sd <- sd(d$years_of_education))
(se <- sd/sqrt(30))
percent_ci <- 95
alpha <- 1 - percent_ci / 100 # alpha = 0.05
lower <- m + qnorm(alpha / 2) * se
```
###Now draw another 99 random samples of 30 zombie apocalypse survivors out and calculate the mean for each of the these samples. Together with the first sample you drew out, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of the sampling distribution for each variable? How do the standard deviations compare to the standard errors estimated in the question about and to those calculated using the population standard deviation? What do these sampling distributions look like? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?

###draw 99 more random samples of 30 zombies out
```
zsamp2<-NULL
zsamp2[[i]]<-NULL
for (i in c(1:99)) {
  zomsamp2[[i]]<- sample_n(d, 30, replace = TRUE)
  }  
  
```
###Calculate the means for each.
```
zsamp2<-as.data.frame(zsamp2)
znew<-dplyr::select_if(zsamp2, is.numeric)
znew<-sapply(znew, mean) 
znew<-t(znew) 
znew<-as.data.frame(wow)
zweight<- znew[,grep("weight", colnames(wow))] 
zweight 
zheight<-znew[,grep("height", colnames(wow))] 
zheight 
zage<-znew[,grep("age", colnames(wow))] 
zage 
zkill<-znew[,grep("zombies_killed", colnames(wow))] 
zkill 
zed<-znew[,grep("years_of_education", colnames(wow))] 
zed
```

###What are the means and standard deviations of the sampling
distribution for each variable?
```
tzweight<-sum(zsamp2[,grep("weight", colnames(zsamp2))]) + sum(new_sample$weight)
tzheight<-sum(zsamp2[,grep("height", colnames(zsamp2))]) + sum(new_sample$height) 
tzomage<-sum(zsamp2[,grep("age", colnames(zsamp2))]) + sum(new_sample$age) 
tzkill<-sum(zsamp2[,grep("zombies_killed", colnames(zsamp2))]) + sum(new_sample$zombies_killed)
tzed<-sum(zsamp2[,grep("years_of_education", colnames(zsamp2))]) + sum(new_sample$years_of_education)
```
### Means for each variable

```
#mean weight
z1<-(tzweight)/3000
z1 
#mean height
z2<-(tzheight)/3000
z2 
#mean age
z3<-(tzage)/3000
z3 
#mean zombies killed
z4<-(tzkill)/3000
z4 
#mean years educated
z5<-(tzed)/3000
z5 #mean years educated
```

###Sd for each variable
```
tzweight2<-cbind(zomsamp2[,grep("weight", colnames(zomsamp2))], zomsamp$weight) 
tzheight2<-cbind(zomsamp2[,grep("height", colnames(zomsamp2))], zomsamp$height)
tzage2<-cbind(zomsamp2[,grep("age", colnames(zomsamp2))], zomsamp$age)
tzkill2<-cbind(zomsamp2[,grep("zombies_killed", colnames(zomsamp2))], zomsamp$zombies_killed)
tzed2<-cbind(zomsamp2[,grep("years_of_education",colnames(zomsamp2))],
zomsamp$years_of_education) 
```
###gather into one matrix column
```
tzweight2<-gather(tzomweight2)
tzweight2<-dplyr::select_if(tzomweight2, is.numeric)
tzweight2<-as.matrix(tzomweight2)
tzheight2<-gather(tzomheight2) 
tzheight2<-dplyr::select_if(tzomheight2, is.numeric)
tzheight2<-as.matrix(tzomheight2)
tzage2<-gather(tzomage2) 
tzage2<- dplyr::select_if(tzomage2, is.numeric)
tzage2<-as.matrix(tzomage2)
tzkill2<-gather(tzomzom2) 
tzkill2<- dplyr::select_if(tzomzom2, is.numeric)
tzkill2<-as.matrix(tzomzom2)
tzed2<-gather(tzomed2) 
tzed2<-  dplyr::select_if(tzomed2, is.numeric)
tzed2<-as.matrix(tzomed2)
```
###SD Function
```
zomsd <- function(x) {
  sqrt(sum((x - mean(x))^2)/100-1)
}
```
###calculate sd for each variable
```
zsdw<-zomsd(tzomweight2)
zsdw 
zsdh<-zomsd(tzomheight2)
zsdh 
zsda<-zomsd(tzomage2)
zsda 
zsdkill<-zomsd(tzkill2)
zsd 
zsded<-zomsd(tzed2)
z 
```








